Clustering time series based on probability distributions across temporal granularities

### 2021-11-16 main.Rmd
small tweak

```{r external, include = FALSE, cache = FALSE}
#knitr::read_chunk('script/main.R')
knitr::read_chunk('script/mylibrary.R')
knitr::read_chunk('script/mytheme.R')
knitr::read_chunk('script/application.R')
knitr::read_chunk('script/application.R')
knitr::read_chunk('script/validation.R')
```

>>>>

```{r external, include = FALSE, cache = FALSE}
#knitr::read_chunk('script/main.R')
knitr::read_chunk('script/mylibrary.R')
knitr::read_chunk('script/mytheme.R')
knitr::read_chunk('script/application.R')
knitr::read_chunk('script/validation.R')
```
